Verification of Stencil Computations with Spatial Specifications

### 2016-10-15 new-intro.tex
Reference to evaluation section in contributions

\item we report on a quantitative study of stencil computations on a
  corpus of numerical Fortran programs (ranging from small to large),
  totalling one million lines of code. Our tool identifies and infers
  specifications for 35,000 stencil computations in the
  corpus. Approximately 10\% of the stencils we found are non-trivial,
  corresponding to code which is a possible source of errors. This
  validates our hypothesis that the majority of stencil computations have a
  regular shape, and validates the design of our language in its
  capability to capture many core patterns.

>>>>

\item we report on a quantitative study of stencil computations on a
  corpus of numerical Fortran programs (ranging from small to large)
  (Section~\ref{sec:evaluation}), totalling one million lines of code. Our tool
  identifies and infers specifications for 35,000 stencil computations in the
  corpus. Approximately 10\% of the stencils we found are non-trivial,
  corresponding to code which is a possible source of errors. This validates
  our hypothesis that the majority of stencil computations have a regular
  shape, and validates the design of our language in its capability to capture
  many core patterns.
